An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-29 main.tex
Add discussion to resistance section.

    Fixation probabilities for Moran processes are obtained for 172
    different strategies. This is done in both a standard 200 turn
    interaction and a noisy setting.

@@

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). It then either
        cooperates or defects for all rounds~\cite{Li2009}.  This strategy was
        specifically designed for Evolutionary processes so it is perhaps also
        not surprising that it does well here.
    \item The finite state machine stragegy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_12_resist.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

>>>>

    Fixation probabilities for Moran processes are obtained for 164
    different strategies.

@@

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). As long as the
        opponent plays the same handshake and does not defect in the future it
        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
        strategy was specifically designed for Evolutionary processes so it is
        perhaps also not surprising that it does well here.
    \item The finite state machine stragegy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

Figures~\ref{fig:fixation_heatmap_resist} show \(x_{N-1}\)
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that as the population size \(N\) increases the
probability of resistance increases.
This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
showing the median fixation as well as the neutral fixation for each given
scenario.

@@

Table~\ref{tbl:top_five_resist} shows the top five strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 12\}\).
% TODO Change 12 to 14
Once again none of the short memory strategies from
Section~\ref{sec:two_individuals} perform well for high \(N\).

Three strategies have both high \(x_1\) and high \(x_{N-1}\):

\begin{itemize}
    \item Collective;
    \item Predator;
    \item Prober 4
\end{itemize}

However, Remorseful Prober, Worse and Worse 2 and Tester no longer do as well.
There are two strategies that are only top performers in \(x_{N-1}\):

\begin{itemize}
    \item Handshake: a slightly less aggressive version of the Collective
        strategy \cite{robson1989}. As long as the initial sequence is played
        then it cooperates. Thus it will do well in a population consisting of
        many members of itself: just as the Collective strategy does. However it
        is not aggressive enough to invade other populations.
    \item Winner 21: a strategy that makes it's decision deterministically based
        on 1 round of it's own strategy and 2 of the opponents strategy
        \cite{Mathieu2015}.
\end{itemize}
% TODO Revise this if need be for N=14

Interestingly none of these strategies are deterministic: this is explained by
the need of strategies to have a steady hand when interacting with their own
kind. In essence: acting stochastically increase the chance of friendly fire.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{./tex/summary_top_12_resist.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five resistors}
    \label{tbl:top_five_resist}
\end{table}

It is evident through
Sections~\ref{sec:two_individuals},~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors} that performance of strategies not only depends
on the initial population distribution but also that there seems to be a
difference depending on whether or not \(N>2\). This will be explored further in
the next section.
